Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-12-13 Manuscript/Manuscript.Rmd
Add note about univariate missingness in popularity data

```{r pop, echo=FALSE, message=FALSE, warning=FALSE}
# load data and merge classes into schools for this tutorial -> but this cannot work because how texp and popteach are defined...
pop <- readRDS("../Data/popNCR2.RDS") %>% mutate(class = as.factor(class))

@@

The missingness in this dataset is induced conform MAR and MNAR mechanisms. The missing data pattern, Figure \ref{fig:pop_pat}, shows the systematic nature of the missingness.

>>>>

```{r pop, echo=FALSE, message=FALSE, warning=FALSE}
# load data 
pop <- readRDS("../Data/popNCR2.RDS") %>% mutate(class = as.factor(class))

@@

The missingness in this dataset is induced conform MAR and MNAR mechanisms. The missing data pattern, Figure \ref{fig:pop_pat}, shows that just one variable is incomplete **[the next part is not yet updated to reflect this]**.
